---
title: "ufoSightings"
author: "Benjamin C. Dean"
date: "25/06/2019"
output: rmarkdown::github_document
---

This is the TidyTuesday for the week of 25 June 2019. This week's dataset is all about UFO sightings over the past few decades. 

```{r}
ufo_sightings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-25/ufo_sightings.csv")

library(tidyverse)
library(gganimate)
library(maps)
library(lubridate)
library(ggplot2)
library(gifski)
```

## Explore and clean the data

```{r} 
ufo_sightings
names(ufo_sightings)

ufo_sightings$date_documented <- mdy(ufo_sightings$date_documented)

ufo_sightings$date_time <-parse_date_time(ufo_sightings$date_time, "m/d/y HM")

```

## Explore shape of ufos
An unusual field is the shape of the UFO. I wonder how many shapes there are and which are the most commonly sighted? 

```{r} 

ufo_sightings %>%
  count(ufo_shape) %>%
  arrange(desc(n)) %>%
  top_n(10) %>%
  ggplot(aes(reorder(ufo_shape, n), n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title="Top 10 shapes of UFOs by number of sightings") +
  labs(x="Shape of UFO", y="$ of sightings")
  theme_minimal() 

```

## Mapping
With a dataset like this, with longitude and latitutde, we should try and map the sightings over time.

```{r}
# Tried to get just the data for Australia - however I still do not have a means by which to map them just on a map of Australia

# next time try: https://medium.com/@mueller.johannes.j/use-r-and-gganimate-to-make-an-animated-map-of-european-students-and-their-year-abroad-517ad75dca06

#Aus <- ufo_sightings %>%
#  filter(country == "au") 

world <- ggplot() +
  borders("world", colour = "gray85", fill = "gray80") +
  theme_map() 

map <- world +
  geom_point(aes(x = longitude, y = latitude),
             data = ufo_sightings, 
             colour = 'purple', alpha = .5) +
  labs(title = 'UFO sightings in year: {frame_time}') +
  transition_time(date_time) +
  ease_aes('linear')

map

anim_save("ufo.gif", map)
```
