---
title: "Revenues from major media franchises"
author: "Benjamin C. Dean"
date: "03/07/2019"
output: 
  html_document:
    keep_md: true
---

This is the TidyTuesday for the week of 3 July 2019. This week's dataset is about the revenues generated by major media companies over the past few decades.  

As a reminder, the idea is to take a new dataset each week and create something interesting within an hour.

https://github.com/rfordatascience/tidytuesday

## Set-up workspace
Import libraries, data and preliminary cleaning. 

```{r, warning = F, message = FALSE} 

library(tidyverse)
library(stringr)
library(data.table)

```

```{r, warning = F, message = F}

media_franchises <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-07-02/media_franchises.csv")

media_franchises$revenue_category <- as.factor(media_franchises$revenue_category)

```

## Examine data
We take a look at what we're working with. Interestingly there are revenue categories, the respective revenues and the owners/creators of the respective franchises. 

```{r}

view(media_franchises)
glimpse(media_franchises)

```

## Analysis
What were the top sources of revenue over the years? The answer is 'Merchandise, licensing and retail'. 
```{r, warning = F} 

media_franchises %>%
  group_by(revenue_category) %>% 
  summarise(revenue = sum(revenue)) %>%
  arrange(desc(revenue)) %>%
  ggplot(aes(reorder(revenue_category, revenue), revenue)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title="Top sources of revenue") +
  labs(x="Source of revenue", y="Revenue in billions") +
  theme_minimal() 

```

Which owners have made the most money? The Walt Disney company, by far, followed by Nintendo.

```{r, warning = F}

media_franchises %>%
  group_by(owners) %>% 
  summarise(revenue = sum(revenue)) %>%
  arrange(desc(revenue)) 
```

Which creators have created the most value? 

```{r, warning = F}
media_franchises %>%
  group_by(creators) %>% 
  summarise(revenue = sum(revenue)) %>%
  arrange(desc(revenue)) 
```

Let's  break down the Pokémon-related brands by revenue over the years.

```{r, warning = F} 

media_franchises %>%
  filter(str_detect(owners, 'Pokémon')) %>%
  ggplot(aes(revenue_category, revenue)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title="Pokémon: Top sources of revenue") +
  labs(x="Source of revenue", y="Revenue in billions") +
  theme_minimal() 
 

```

Let's do it again for Nintendo as a whole - but see if we can add a color layer to the franchises. 

```{r, warning = F} 

media_franchises %>%
  filter(str_detect(owners, 'Nintendo')) %>%
  ggplot(aes(revenue_category, revenue, fill = franchise)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title="Nintendo: Top sources of revenue") +
  labs(x="Source of revenue", y="Revenue in billions") +
  theme_minimal() 

```


```{r}

media_franchises %>%
  filter(str_detect(owners, 'Nintendo')) %>%
  ggplot(aes(franchise, revenue, fill = revenue_category)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title="Nintendo: Top sources of revenue") +
  labs(x="Source of revenue", y="Revenue in billions") +
  scale_fill_discrete(name = "Category of revenue") +
  theme_minimal() 
 
```

