---
title: "meteorites"
author: "Benjamin C. Dean"
date: "11/06/2019"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
theme_set(theme_light())

meteoritesRaw <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-11/meteorites.csv")
```

Exploring the dataset.

```{r}
meteoritesRaw
View(meteoritesRaw)
```

We have a variable that covers the mass of the meteorites. Interestingly they follow a skew distribution. We can use the psych package to derive the skew and kurtosis. This all suggests that this variable should be log transformed (depending on the analysis we decide to do). 

```{r}
library(psych)
describe(meteoritesRaw$mass)
hist(log(meteoritesRaw$mass))

```

It might be interesting to see if there is some relationship between when the meteorite was found and its size. We'd assume that the time/year it was found would be independent of the size - but it might still be fun to see what comes out. We'll need to bucket the years by decade to make the analysis more interpretable.

Interestingly the distribution has changed since 1960. Perhaps the recording of meteorites has gotten better, which has resulted in more smaller meteorites being recorded. 

Also - what is the deal with the meteorite that hit in 2100??? Whoops NASA! 

```{r}
meteoritesDecade <- meteorites %>%
  filter(year > 1899) %>%
  mutate(decade = year - (year %% 10)) %>%
  group_by(decade) %>%
  filter(!is.na(decade)) %>%
  ggplot(aes(group = decade, x = decade, y = mass)) +
  geom_boxplot() +
  scale_y_log10() + 
  labs(title = "Distribution of mass of meteorites that were found on earth from 1900 - 2019",
       subtitle = "Log transformed mass",
       x = "Decade",
       y = "Mass of meteorite") +
  coord_flip(); meteoritesDecade

?filter
```

There's some geocoded variables. Time has run-out but I was attempting to cook up a map of Australia and plot the meteorites found there. The issue I ran into had to do with plotting the dots on a rectangle, which ggmap doesn't like in a data frame. Better luck next time! [For other people's submissions it looks like I should have delved into gganimate].

```{r}
library(maps)
library(mapdata)
library(ggmap)

map <- get_map(location = c(left = 115.8605761, bottom = 42.0853657, right = 153.61194, top = -19.2576), zoom = 3)

meteoritesMap <- meteoritesRaw %>%
  filter(!is.na(long && lat)) %>%
  ggmap(map) +
  geom_point(aes(x = long, y = lat), size = 10, data = meteoritesMap)

```


